Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-08-31 reanalysis-4-propensity_scores.qmd
run ps
mem issues

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "test"  # Should match imputation mode

@@

# Set up parallel processing
n_cores <- detectCores() - 1  # Use all cores except one
log_message(paste0("Parallel processing: Using ", n_cores, " cores"))

>>>>

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "final"  # Should match imputation mode

# PARALLEL PROCESSING CONFIGURATION
max_cores_for_ps <- 3  # Maximum cores to use for propensity score estimation (memory-intensive)

@@

# Set up parallel processing
# Reduce cores for memory-intensive GBM models
available_cores <- detectCores()
# Use fewer cores to avoid memory issues - each GBM model needs substantial memory
n_cores <- min(max_cores_for_ps, available_cores - 1)  # Use configured max cores to ensure sufficient memory per worker
log_message(paste0("Parallel processing: Using ", n_cores, " cores (of ", available_cores, " available) to manage memory usage"))
